The Right Way to Search Evolving Graphs

### 2016-03-04 paper.tex
clarify causal edges in the experiment

We generate a sequence of random (directed) \texttt{IntEvolvingGraph}s
with $10^5$ active nodes and $10$ time stamps.
The first \texttt{IntEvolvingGraph} in the sequence has about
$10^8$ static edges.
We consecutively add new
random static edges to this \texttt{IntEvolvingGraph}. For example,
the second random \texttt{IntEvolvingGraph} in the sequence
has about $1.5 \times 10^8$ static edges and the third
has $1.8 \times 10^8$ static edges.
% At each time stamp $i$, a static edge is included in $G^{[i]} \in G_4$ with
% probability $p$.
Note that in this experiment, we do not have direct control
over the full edge set $E$, only the static edge set $\tilde E$. However, the
causal edge set $E'$ can grow at most by $O(\tilde E)$, so it suffices to demonstrate
linear scaling in $|\tilde E|$.
Figure \ref{fig:time} shows the plots of number of edges against the computation time
for running Algorithm \ref{alg:bfs} in Julia. All experiments are conducted
on a single core of a Linux system with an Intel(R) Xeon(R) E7-8850 CPU running
at 2.00 GHz clock speed.
The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with the result of Theorem \ref{thm:complexity}.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.58]{time.pdf}
  \caption{Experimental run time of Algorithm \ref{alg:bfs}
on a collection of random evolving graphs with $1.0\times 10^5$ active nodes and $10$ time
stamps, showing linear scaling in $|\tilde E|$. The horizontal axis shows the
number of edges ($|\tilde E|$, including only the static edges) of each evolving
graph, while the vertical axis shows the corresponding
computation time.}
  \label{fig:time}
\end{figure}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.

>>>>

We generate a sequence of random (directed) \texttt{IntEvolvingGraph}s
with $10^5$ active nodes and $10$ time stamps.
The first \texttt{IntEvolvingGraph} in the sequence has about
$10^8$ static edges.
We consecutively add new
random static edges to this \texttt{IntEvolvingGraph}. For example,
the second random \texttt{IntEvolvingGraph} in the sequence
has about $1.5 \times 10^8$ static edges and the third
has $1.8 \times 10^8$ static edges.
% At each time stamp $i$, a static edge is included in $G^{[i]} \in G_4$ with
% probability $p$.
Note that in this experiment, we do not have direct control
over the full edge set $E$, only the static edge set $\tilde E$. 
When we add new static edges, new causal edges may be added as well
(if the corresponding temporal nodes were not active before).
However, the number of newly introduced causal edges for each active node 
is bounded by the number of time stamps, so it suffices to demonstrate
linear scaling in $|\tilde E|$.
Figure \ref{fig:time} shows the plots of number of edges against the computation time
for running Algorithm \ref{alg:bfs} in Julia. All experiments are conducted
on a single core of a Linux system with an Intel(R) Xeon(R) E7-8850 CPU running
at 2.00 GHz clock speed.
The results show Algorithm \ref{alg:bfs} can be computed in linear time, which agrees
with the result of Theorem \ref{thm:complexity}.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.58]{time.pdf}
  \caption{Experimental run time of Algorithm \ref{alg:bfs}
on a collection of random evolving graphs with $10^5$ active nodes and $10$ time
stamps, showing linear scaling in $|\tilde E|$. The horizontal axis shows the
number of edges ($|\tilde E|$, including only the static edges) of each evolving
graph, while the vertical axis shows the corresponding
computation time.}
  \label{fig:time}
\end{figure}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing.
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
% \texttt{IntMatrixList}, a data type in EvolvingGraphs.jl, represents an evolving graph
% as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
% We can convert an \texttt{IntMatrixList} to its corresponding block adjacency matrix
% using the function \texttt{spmatrix}.
